---
title: "Test2"
author: "Nate"
date: "June 13, 2018"
output: pdf_document
---

## This is markdown here 
f
# Steps for creating Rmarkdown

1. New File > Text 
2. Save with .Rmd extension

* Bullet list 
* with bullet points

_italic_
**bold**

_ this doesn't work _ 


_this does work_ 


# Important! 

You can't re-use 'chunk' names. 

```{r 1b}
# In this section you can only do R -code 

# Generate random normal data
hist(rnorm(100))

```


## New section : Lab 

1. Loading data set 
2. Run Regression 
3. Interpretation 

```{r lab}
library(ISLR)
library(MASS)

# load data
data(Boston)
str(Boston)
dim(Boston)
?Boston
```

### Fit a model 

```{r }
# Lm formula
fit.lm1 <- lm(medv ~ crim, data=Boston)
summary(fit.lm)
```

Coefficient for crime is -0.415. 
* Negative relationship
* Units of crime is per/capital crime rate
* Units of medv is 1000$ per unit 

Interpretation of coefficient:

**What is the effect on the response 
variable for a 1-unit change in the predictor variable, 
holding all other variables constant.**

One unit change in crim (=one percentage change in crime rate)
corresponds to a DROP of -0.415*1000 in median house values. 

```{r}
# range of prices
range(Boston$medv)*1000

```

```{r}
confint(fit.lm1)

```

```{r}
# Base R plot with fit model
plot(Boston$crim, Boston$medv, 
                  col="darkcyan", 
                  main="Median housing values vs. Crime")
abline(fit.lm1, col="gray5")

```

```{r}
hist(Boston$medv)
```
```{r}
hist(Boston$crim)
```



