---
title: "Test2"
author: "Nate"
date: "June 13, 2018"
output: pdf_document
---

## This is markdown here 
f
# Steps for creating Rmarkdown

1. New File > Text 
2. Save with .Rmd extension

* Bullet list 
* with bullet points

_italic_
**bold**

_ this doesn't work _ 


_this does work_ 


# Important! 

You can't re-use 'chunk' names. 

```{r 1b}
# In this section you can only do R -code 

# Generate random normal data
hist(rnorm(100))

```


## New section : Lab 

1. Loading data set 
2. Run Regression 
3. Interpretation 

```{r lab}
library(ISLR)
library(MASS)

# load data
data(Boston)
str(Boston)
dim(Boston)
?Boston
```

### Fit a model 

```{r }
# Lm formula
fit.lm1 <- lm(medv ~ crim, data=Boston)
summary(fit.lm)
```

Coefficient for crime is -0.415. 
* Negative relationship
* Units of crime is per/capital crime rate
* Units of medv is 1000$ per unit 

Interpretation of coefficient:

**What is the effect on the response 
variable for a 1-unit change in the predictor variable, 
holding all other variables constant.**

One unit change in crim (=one percentage change in crime rate)
corresponds to a DROP of -0.415*1000 in median house values. 

```{r}
# range of prices
range(Boston$medv)*1000

```

```{r}
confint(fit.lm1)

```

```{r}
# Base R plot with fit model
plot(Boston$crim, Boston$medv, 
                  col="darkcyan", 
                  main="Median housing values vs. Crime")
abline(fit.lm1, col="gray5")

```

```{r}
hist(Boston$medv)
```
```{r}
hist(Boston$crim)
```

The crime rate data looks like an _exponential_ distribution. 

We'll redo the model with the inverse of the exponential, a log transform, and compare the fit. 

```{r}
fit.lm2 <- lm(medv ~ log(crim), data=Boston) 
summary(fit.lm2)
```

The $R^2$ value has imporved to 0.2 from 0.15. 

Below is a plot of the log of the crime rate against house value.

```{r}
# Base R plot with fit model
plot(log(Boston$crim), Boston$medv, 
                  col="darkcyan", 
                  main="Median housing values vs. Crime")
abline(fit.lm2, col="gray5", lwd = 2, lty = 2)

```


It looks like the higher home values follow a different trend. 
There seems to be no relation of crime rate to some of the highest priced houses.

```{r}
Boston2 <- Boston[Boston$medv < 40, ]

fit.lm3 <- lm(medv ~ log(crim), data=Boston2) 
summary(fit.lm3)
```

Removing the high priced houses gives us an $R^2$ close to 0.4, almost doubling the previous fit. 

This means that for most housing, crime rates are very closely associated with 

Below is a plot of the log of the crime rate against house value.

```{r}
# Base R plot with fit model
plot(log(Boston2$crim), Boston2$medv, 
                  col="darkcyan", 
                  main="Median housing values vs. Crime Rate")
abline(fit.lm3, col="gray5", lwd = 2, lty = 2)

```

What about the higher priced houses that we omitted from the above analysis? 

```{r}
Boston3 <- Boston[Boston$medv > 40, ]

fit.lm4 <- lm(medv ~ log(crim), data=Boston3) 
summary(fit.lm4)
```

The results confirm that there is no relationship between the highest priced houses and crime. 
This result doesn't seem that intuitive and to me it would make it worth looking at the actual data to see if
there is a problem with the data. 



```{r}
# Base R plot with fit model
plot(log(Boston3$crim), Boston3$medv, 
                  col="darkcyan", 
                  main="Median housing values vs. Crime Rate")
abline(fit.lm4, col="gray5", lwd = 2, lty = 2)
```


The suspicious looking data points are all at 50K 

```{r}
library(GGally)
suspect <- Boston[Boston$medv == 50, ]
#ggpairs(suspect)
names(suspect) <- paste0("X", 1:ncol(suspect))
#pairs(suspect)

```





